Learning From Massive Noisy Labeled Data for Image Classification

### 2015-04-08 paper.tex
Merge tables

We list all the experiment settings in Table~\ref{tab:models}. Different methods require different training data. We use only the clean data $\mathcal{D}_c$ to get the baselines under strong supervisions. On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}. Meanwhile, the noisy labels of $\mathcal{D}_n$ are treated as ground truths for AlexNet, and are discarded for Pseudo-Label.

In general, we use a mini-batch size of $256$. The learning rate is initialized to be $0.001$ and is divided by $10$ after every $50,000$ iterations. We keep training each model until convergence. Classification accuracies on both the validation and test set are presented in Table~\ref{tab:accuracy}.

\begin{table}
\begin{center}
\begin{tabular}{c|p{3.5em}|p{9em}|p{5em}}
\hline
\# & Method & Training Data & Initialization \\
\hline\hline
1 & AlexNet & $\mathcal{D}_c$ & random \\
\hline
2 & AlexNet & $\mathcal{D}_c$ & ImageNet pretrained \\
\hline
3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & random \\
\hline
4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & ImaegNet pretrained \\
\hline
5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & model \#2 \\
\hline
6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as unlabeled & model \#2 \\
\hline
7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 \\
\hline
8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 \\
\hline
\end{tabular}
\end{center}
\caption{Experiment settings}
\label{tab:models}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
\hline
\# & Validation Accuracy & Test Accuracy \\
\hline\hline
1 & 64.28\% & 64.54\% \\
\hline
2 & 72.21\% & 72.63\% \\
\hline
3 & 73.76\% & 74.03\% \\
\hline
4 & 75.06\% & 75.13\% \\
\hline
5 & 75.57\% & 75.30\% \\
\hline
6 & 73.10\% & 73.04\% \\
\hline
7 & 75.97\% & 76.22\% \\
\hline
8 & \textbf{77.65\%} & \textbf{78.24\%} \\
\hline
\end{tabular}
\end{center}
\caption{Classification accuracies on validation and test set}
\label{tab:accuracy}
\end{table}

@@

Finally, row \#7 and \#8 show the effect of modeling the label noise. Model \#7 is only $0.4\% \sim 0.9\%$ better than the baseline model \#5, while our method gains improvement of $2.1\% \sim 2.9\%$. This result does credit to our image dependent label noise model, which fits better to the noisy labeled data crawled from the Internet.

>>>>

We list all the experiment settings in Table~\ref{tab:exp}. Different methods require different training data. We use only the clean data $\mathcal{D}_c$ to get the baselines under strong supervisions. On the other hand, when all the data are used, we upsample the clean data as discussed in Section~\ref{sec:deep_learning_from_noisy_labels}. Meanwhile, the noisy labels of $\mathcal{D}_n$ are treated as ground truths for AlexNet, and are discarded for Pseudo-Label.

In general, we use a mini-batch size of $256$. The learning rate is initialized to be $0.001$ and is divided by $10$ after every $50,000$ iterations. We keep training each model until convergence. Classification accuracies on the test set are presented in Table~\ref{tab:exp}.

\begin{table*}[t]
\begin{center}
\begin{tabular}{c|c|c|c|c}
\hline
\# & Method & Training Data & Initialization & Test Accuracy\\
\hline\hline
1 & AlexNet & $\mathcal{D}_c$ & random & 64.54\% \\
2 & AlexNet & $\mathcal{D}_c$ & ImageNet pretrained & 72.63\% \\
3 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & random & 74.03\% \\
4 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & ImaegNet pretrained & 75.13\% \\
5 & AlexNet & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as ground truths & model \#2 & 75.30\% \\
6 & Pseudo-Label\cite{lee2013pseudo} & upsampled $\mathcal{D}_c$ and $\mathcal{D}_n$ as unlabeled & model \#2 & 73.04\% \\
7 & Bottom-Up~\cite{sukhbaatar2014learning} & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 & 76.22\% \\
8 & Ours & $\mathcal{D}_c$ and $\mathcal{D}_n$ & model \#2 & \textbf{78.24\%} \\
\hline
\end{tabular}
\end{center}
\caption{Experiment results on the collected dataset}
\label{tab:exp}
\end{table*}

% \begin{table}
% \begin{center}
% \begin{tabular}{c|c|c}
% \hline
% \# & Validation Accuracy & Test Accuracy \\
% \hline\hline
% 1 & 64.28\% & 64.54\% \\
% \hline
% 2 & 72.21\% & 72.63\% \\
% \hline
% 3 & 73.76\% & 74.03\% \\
% \hline
% 4 & 75.06\% & 75.13\% \\
% \hline
% 5 & 75.57\% & 75.30\% \\
% \hline
% 6 & 73.10\% & 73.04\% \\
% \hline
% 7 & 75.97\% & 76.22\% \\
% \hline
% 8 & \textbf{77.65\%} & \textbf{78.24\%} \\
% \hline
% \end{tabular}
% \end{center}
% \caption{Classification accuracies on validation and test set}
% \label{tab:accuracy}
% \end{table}

@@

Finally, row \#7 and \#8 show the effect of modeling the label noise. Model \#7 is only $0.9\%$ better than the baseline model \#5, while our method gains improvement of $2.9\%$. This result does credit to our image dependent label noise model, which fits better to the noisy labeled data crawled from the Internet.
